Drought-sensitive trees survive on deep-water access in a tropical forest community

### 2020-08-29 manuscript.rmd
1. Removed community level curves for 200+ species and moved figure for curves on obs species there. 2. Removed corresponding param table 3. Removed figures for leaf vulnerability curves fit to data on individual species 4. Removed figures on trade-offs beetween K and Psi80 for both leaf and stem

## Leaf Vulnerability Curves
\
For the leaf vulnerability curve parameters $A$ & $B$ fitted to the observed data on $K_{leaf}$ vs. $\Psi_{leaf}$, $WSG$ & parameter $B$ explained a large proportion of variation in parameter $A$ (Eq. \@ref(eq:a-mod); *Adj. R*^2^ = `r afit.r2`; *P* `r  afit.p`; also see Fig. S\@ref(fig:ab-fit)). $WSG$ & $LMA$ explained a large proportion of variation in parameter $B$ (Eq. \@ref(eq:b-mod); Adj. *R*^2^ = `r bfit.r2`; *P* `r  bfit.p`). WSG alone explained `r round(a.wsg.r2*100,0)` % of variation in $A$ ($A = `r a.wsg.cf[1]` `r a.wsg.cf[2]`B + `r a.wsg.cf[3]`B^2 + error$; *P* `r  a.wsg.p`) and `r round(b.wsg.r2*100,0)` % of variation in $B$ ($B = `r b.wsg.cf[1]` `r b.wsg.cf[2]`B + `r b.wsg.cf[3]`B^2 + error$; *P* `r  b.wsg.p`). Parameter $B$ alone explained `r round(a.b.r2*100,0)` % of variation in $A$ (*P* `r  a.b.p`), while $LMA$ alone was weakly related to $A$ and was not related to $B$ (not shown). The leaf vulnerability curves fitted to observed data on `r length(sp.exp.param$sp)` species are shown in Figs. S\@ref(fig:leaf-vcurves-data1), S\@ref(fig:leaf-vcurves-data2) and S\@ref(fig:obs-plc-curves) and those predicted for the `r length(unique(data.model.AB$sp))` species in the community are shown in Fig. \@ref(fig:comm-vuln-curves). Corresponding parameters for the community are given in Table S\@ref(tab:param) (also see Fig. \@ref(fig:comm-plc-curves)).

```{r comm-vuln-curves, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "50%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-comm-vuln-curves}Modelled 'vulnerability curves' ($K_{leaf}$ vs. $\\Psi_{leaf}$) at community-scale (", length(data.model.AB$sp)," species) based on data on $WSG$ & $LMA$ and their relationships with vulnerability curve parameters measured on ", length(sp.exp.param$sp)," species. Each line represents a species, color coded by $WSG$ with blue tones indicating smaller values of $WSG$ and red tones indicating larger values of $WSG$.")}

knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/kmax_by_psi/Leaf/kmax_by_psi_color_by_SG100C_AVG_predicted_AB.jpeg"))
```

@@

```{r leaf-vcurves-data1, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "100%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-leaf-vcurves-data}Fitted curves vs. observed data on $K_{leaf}$ vs. $\\Psi_{leaf}$ for ", length(sp.exp.param$sp)," tree species from BCI. Curves are color coded by the model used. AICc for each model are given in inset (RCT:Add models and their reference). Only nine species are shown here. The remaining twelve species are shown in Fig. \\@ref(fig:leaf-vcurves-data2).")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/kmax_by_psi/Leaf/vcurves_fits_to_data_by_sp.1.jpeg"))
```

```{r leaf-vcurves-data2, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "90%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-leaf-vcurves-data}See Fig. \\@ref(fig:leaf-vcurves-data1) caption.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/kmax_by_psi/Leaf/vcurves_fits_to_data_by_sp.2.jpeg"))
```

@@

```{r comm-plc-curves, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "50%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-comm-plc-curves}Modelled 'vulnerability curves' ($K_{leaf}$ vs. $\\Psi_{leaf}$) at the community-scale (", length(ab.table$Species)," species) predicted from soft traits, $WSG$ and $LMA$, with equations \\@ref(eq:a-mod) and \\@ref(eq:b-mod) in absolute terms (A, B) as well as in terms of loss of conductivity (%) (C, D). Each line represents a species, color coded by $WSG$ (A, C), or $LMA$ (B, D), with blue tones indicating smaller values and red tones indicating larger values of $WSG$, or $LMA$.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/kmax_by_psi/Leaf/plot.comm.plc.jpeg"))
```

@@

```{r se-trade-offs, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "100%", fig.pos = 'H', results = "asis", fig.cap = paste0("\\label{lab-se-trade-offs}Efficiency-safety trade-off between $K_{max,~leaf}$ and $\\Psi_{88, leaf}$ (A) and $K_{max,~stem}$ and $\\Psi_{88,~stem}$ based on observed data on ", length(sp.exp.param$sp)," species and ", length(hyd$KmaxS[!is.na(hyd$KmaxS)]), " species, respectively. The fitted equations of the form, $K_{max}$ = a + b.log($\\Psi_{88}$), are given in inset along with goodness-of-fit (*R*^2^) and *p*-values.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/kmax_by_psi/leaf.stem.trade_off.jpeg"))
```

@@

#####
```{r ab-param, results = 'asis', echo = FALSE}
knitr::kable(ab.table, caption = 'Modelled parameters A & B for leaf vulnerability curves ($K_{leaf}$ vs. $\\Psi_{leaf}$) for 233 species in Panama predicted from soft traits, $WSG$ and $LMA$, using Eqs. \\@ref(eq:a-mod) and \\@ref(eq:b-mod). Corresponding curves are of the exponetial form as in Eq. \\@ref(eq:vc-exp).', booktabs = TRUE, escape = FALSE)
```

>>>>

## Leaf Vulnerability Curves
\
For the leaf vulnerability curve parameters $A$ & $B$ fitted to the observed data on $K_{leaf}$ vs. $\Psi_{leaf}$, $WSG$ & parameter $B$ explained a large proportion of variation in parameter $A$ (Eq. \@ref(eq:a-mod); *Adj. R*^2^ = `r afit.r2`; *P* `r  afit.p`; also see Fig. S\@ref(fig:ab-fit)). $WSG$ & $LMA$ explained a large proportion of variation in parameter $B$ (Eq. \@ref(eq:b-mod); Adj. *R*^2^ = `r bfit.r2`; *P* `r  bfit.p`). WSG alone explained `r round(a.wsg.r2*100,0)` % of variation in $A$ ($A = `r a.wsg.cf[1]` `r a.wsg.cf[2]`B + `r a.wsg.cf[3]`B^2 + error$; *P* `r  a.wsg.p`) and `r round(b.wsg.r2*100,0)` % of variation in $B$ ($B = `r b.wsg.cf[1]` `r b.wsg.cf[2]`B + `r b.wsg.cf[3]`B^2 + error$; *P* `r  b.wsg.p`). Parameter $B$ alone explained `r round(a.b.r2*100,0)` % of variation in $A$ (*P* `r  a.b.p`), while $LMA$ alone was weakly related to $A$ and was not related to $B$ (not shown). The leaf vulnerability curves fitted to observed data on `r length(sp.exp.param$sp)` species are shown in Figs. S\@ref(fig:leaf-vcurves-data1), S\@ref(fig:leaf-vcurves-data2) and S\@ref(fig:obs-plc-curves) and those predicted for the `r length(unique(data.model.AB$sp))` species in the community are shown in Fig. \@ref(fig:comm-vuln-curves). Corresponding parameters for the community are given in Table S\@ref(tab:param) (also see Fig. \@ref(fig:obs-plc-curves)).

@@

@@

@@

@@
